Supervised Learning with Fashion MNIST

### 2017-12-13 article/article.tex
tex

\section{DataSet}

	The Fashion MNIST dataset is composed by 70.000 grayscale(0-255) images of size 28x28 labeled into the following 10 different classes: T-shirt/top, Trouser, Pullover, Dress, Coat, Sandal, Shirt, Sneaker, Bag and Ankle boot.\ref{fig:fashionex} is an example of one of the images in the dataset.

	\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.8]{fashionExample.png}
        \caption{Image Example\label{fig:fashionex}}
    \end{center}
    \end{figure}

    For the implementation we used Python and sklearn\cite{scikitlearn} and tensorflow \cite{tensorflow} libraries. The input for the algorithms are the pixels values.

@@

The current state of art for the Fashion MNIST dataset is a recent one, with 96.3\% accuracy using Wide
Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper}.
We will consider this as the ceiling accuracy for our project.

@@

This algorithm was pretty fast to implement.
Since its training consists in only saving the training set, it is pretty fast.
However, it does take a lot of time to classify each example.

@@

For the SVM we used the Scikit-Learn implementation. We first tested with a 3rd degree polynomial kernel and with a penalty parameter C = 10, since
it was the parameters used for the benchmark. We obtained an accuracy of 87.23\%, which is slightly different from the accuracy described in the benchmark (87,23\%).

@@

We also tested for a gaussian kernel, with parameter C = $10^6$ and gamma = $4 10^-7$ since it achieved good results from previous works.
As expected, we obtained better accuracy, achieving 90.13\% for those parameters.

@@

     The Convolutional Neural Networks (CNNs) are the current state-of-the-art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}. For all tests with CNNs the values of the pixels were divided by 255, so that the values are always between 0 and 1. The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}. We used the same layers and kernel sizes but with more features on each convolutional layer. \ref{fig:lenet5} shows the architecture used for the first CNN test.

@@

    We trained the network for 200 epochs and got an accuracy of 89.02\%, then, to increase the examples in the training set, we added rotations from -5 to 5 degrees and got 89.81\%.

@@

    Our next approach was to use Random Erasing as data augmentation, since it was used in the state-of-the-art implementation. Random Erasing randomly
selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting. For 300 epochs the accuracy was . Seeing that adding only the Random Erasing technique decreased the accuracy, we combined it with the rotation from -5 to 5 degrees.

>>>>

\section{The Dataset}

    The Fashion MNIST dataset is composed by 70.000 grayscale (0-255) images of size 28x28 labeled into the following 10 different classes: T-shirt/top, Trouser, Pullover, Dress, Coat, Sandal, Shirt, Sneaker, Bag and Ankle boot. Figure \ref{fig:fashionex} is an example of one of the images in the dataset.

    For the implementation we used Python and Scikit-Learn \cite{scikitlearn} and TensorFlow \cite{tensorflow} libraries. The input for the algorithms are the pixels values.

    \begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.8]{fashionExample.png}
        \caption{Example of an image in the dataset\label{fig:fashionex}}
    \end{center}
    \end{figure}

@@

The current state of art for the Fashion MNIST dataset is a recent one, with 96.3\% accuracy using Wide
Residual Networks using random erasing data augmentation \cite{randomerasingdataaugmentationpaper} and other image pre-processing techniques.
We will consider this as the ceiling accuracy for our project.

@@

This algorithm was pretty fast to implement.
Since its training consists in only saving the training set, it is pretty fast to train.
However, it does take a lot of time to classify each example.

@@

For the SVM we used the Scikit-Learn implementation. We first tested with a 3rd degree polynomial kernel and with a penalty parameter C = 10, since
they were the parameters used for the benchmark. We obtained an accuracy of 87.23\%, which is slightly different from the accuracy described in the benchmark (89,7\%).

@@

We also tested for a gaussian kernel, with parameter C = $10^6$ and gamma = $4  \cdot 10^{-7}$ since it achieved good results from previous works.
As expected, we obtained better accuracy, achieving 90.13\% for those parameters.

@@

     The Convolutional Neural Networks (CNNs) are the current state of the art for the Fashion-MNIST dataset with 96.3\% accuracy \cite{randomerasingdataaugmentationpaper}. To be able to train faster and with larger networks, we used the GPU NVIDIA GTX 980M with CUDA.

      The first CNN that we used was based on the 1994s LeNet5 \cite{yannLeCun:1998}, one of the first CNNs, that has a 99.05\% accuracy for the MNIST dataset \cite{yannLeCun:mnist}. We used the same layers and kernel sizes but with more features on each convolutional layer. \ref{fig:lenet5} shows the architecture used for the first CNN test.

@@

    We trained the network for 200 epochs and got an accuracy of 89.02\%, then, to increase the examples in the training set, we added rotations from -5 to 5 degrees, degree by degree, and got 89.81\%.

@@

    Our next approach was to use Random Erasing as data augmentation, since it was used in the state-of-the-art implementation. Random Erasing randomly
selects a rectangle region in an image and erases its pixels with random values, which reduces the risk of over-fitting. For 300 epochs the accuracy was .

	\section{Conclusions}

	After running all the different algorithms we could realize the importance of a powerfull resource for processing, in our case the GPU. We also have seen the importance of choosing good pre-processing techniques, that can either boost or decrease the quality of the test.
	Also, we have witnessed the efficiency of the Convolutional Neural Networks for a task of this kind, because they got the higher results sometimes even in less time.

	Our results were above the ones in the benchmark, but still lower than the state of art. The state of art used a more complex network, with more pre-processing, which is what we believe that was the cause for the difference between our accuracy.

	Our next steps to improve the accuracy of the result are to add more data augmentation combined with the Random Erasing (i.e flipping, rotation and cropping) and to implement and test different networks with TensorFlow, such as the ResNet, which is similar to the CNN used in the state of the art implementation.
	We are also extending the currents implementations to more complex data sets like CIFAR-10 and CIFAR-100, that are datasets with 32x32 RGB images with respectively 10 and 100 different labeled classes.
